P versus NP

### 2020-03-10 doc/manuscript.tex
Possibly, the last commit

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency. However, a precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. Another major complexity classes are L and NL. Whether L = NL is another fundamental question that it is as important as it is unresolved. We show if L is equal to NL, then P = NP. In addition, we demonstrate that L is equal to NL. In this way, we prove the complexity class P is equal to NP. Furthermore, we demonstrate the complexity class L is equal to NP.
\end{abstract}

@@

It is fully expected that $P \neq NP$ \cite{Pap03}. Indeed, if $P = NP$ then there are stunning practical consequences \cite{Pap03}. For that reason, $P = NP$ is considered as a very unlikely event \cite{Pap03}. Certainly, $P$ versus $NP$ is one of the greatest open problems in science and a correct solution for this incognita will have a great impact not only in computer science, but for many other fields as well \cite{AS17}. Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}. We show some results that prove this outstanding problem with the unexpected solution of $P = NP$.

@@

\subsection{Preliminaries}

@@

\subsection{Hypothesis}

@@

From the early days of automata and complexity theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}. Each model has a read-only input tape and some work tapes \cite{KU15}. The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}. In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively \cite{KU15}.

Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}. They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions \cite{HM81}. Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$ \cite{HM81}.

@@

\begin{theorem}
\label{pos-implication}
If the Hypothesis \ref{hypothesis2} is true, therefore when $L = NL$, then $P = NP$.
\end{theorem}

\begin{proof}
We can accept the elements of the language $L_{1} \in 1NL$ by a nondeterministic one-way logarithmic space Turing machine $M'$. In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$, where $u$ is placed on the special read-once tape of $M''$. The reason is because we can simulate the output string of $M(w, u)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}. Certainly, we do not need to reset the computation of $M(w, u)$ for the reading at once of a symbol in the output string of $M(w, u)$ by the nondeterministic one-way logarithmic space Turing machine $M'$. Consequently, $M''$ can be converted into a logarithmic space disqualifier for the language $L_{2}$ just assuming that $L = NL$, because of the nondeterministic logarithmic space Turing machine $M''$ could be simulated by a deterministic logarithmic space Turing machine. Therefore, $L_{2}$ is in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$ \cite{Pap03}. If any single $\textit{coNP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{Pap03}. Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L = NL$.
\end{proof}

@@

\begin{proof}
Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right. We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$. While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause from left to right. In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $\textit{SUM--ZERO}$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$. Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
\[\phi \in 3UNSAT \Leftrightarrow (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value, respectively. Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output. This logarithmic space disqualification will be the Algorithm \ref{algorithm2}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$. In addition, we reject immediately when the following comparisons:
\[A[i] < 1 \vee A[i] > 3\]
hold at least into one single binary digit. Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$. In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.

\begin{algorithm}
\caption{Logarithmic space disqualifier}\label{algorithm2}
\begin{algorithmic}[1]
\Comment{A valid instance for $3UNSAT$ with its disqualification}
\Procedure{$\textit{DISQUALIFIER}$}{$\phi, A$}
\Comment{Initialize an index}
\State $j \gets 0$
\Comment{$m$ is the number of clauses in $\phi$}
\Comment{Iterate for the elements of the disqualification array $A$}
\For{$i$}{$1$}{$m + 1$}
\If{$i = m+1$}
\Comment{There exists an $m+1$ element in the array}
\If{$A[i] \neq \textit{undefined}$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\EndIf
\Comment{Break the $\textbf{for}$ loop}
\State \textbf{break}
\ElsIf{$A[i] = \textit{undefined} \vee A[i] < 1 \vee A[i] > 3$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\Else
\State $j \gets A[i]$
\EndIf
\Comment{From the indexed $i^{th}$ clause $c_{i} = (x_{j} \vee y_{k} \vee z_{r})$ in $\phi$}
\Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
\Comment{Output the integer representation of the $j^{th}$ literal, that is $n(x_{j})$}
\Comment{Filled with zeroes to the left until a total of $|3 \times m|$ bits including the literal}
\Comment{But, the bit-length of the symbol minus is ignored in filling the negated literals}
\State \textbf{output} $``\ , \ n(x_{j})"$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{proof}

@@

\begin{proof}
This is a consequence of Theorems \ref{1nl} and \ref{demonstration}.
\end{proof}

\begin{theorem}
\label{equal-NP}
If $L = NL$ then $P = NP$.
\end{theorem}

@@

\subsection{L versus NL}

A directed graph $G = (V, E)$ is topologically sorted when for any pair of edges $(a, b)$ and $(b, c)$ in $G$, then the edge $(a, b)$ is listed before $(b, c)$ \cite{HM81}.

We show a previous known $\textit{NL--complete}$ problem:

\begin{definition}
$\textbf{TAGAP}$

INSTANCE: Given a directed graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$.

QUESTION: Is there a path from $s$ to $t$?

REMARKS: $TAGAP \in \textit{NL--complete}$ \cite{HM81}. Certainly, this problem remains in $\textit{NL--complete}$ even if the graph is not acyclic \cite{HM81}. 
\end{definition}

\begin{definition}
An instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted when for any pair of clauses $(a, b)$ and $(b, c)$ in $\phi$, then the clause $(a, b)$ is listed before $(b, c)$.
\end{definition}

\begin{definition}
$\textbf{TAGAP 2SAT}$

INSTANCE: Given an instance $\phi$ of $\textit{XOR 2SAT}$ that is topologically sorted.

QUESTION: Is there a truth assignment, such that each clause of one literal is satisfied and each clause of two literals has not a true and false evaluated literals at the same time?
\end{definition}

\begin{theorem}
$\textit{TAGAP 2SAT} \in L$.
\end{theorem}

\begin{proof}
We can check whether an instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted in logarithmic space. Certainly, for each clause $(a, b)$ we can verify in logarithmic space whether there is not another clause $(b, c)$ that is listed before of $(a, b)$. In addition, given an instance $\phi$ of $\textit{XOR 2SAT}$ with $m$ clauses, for each clause of two literals $c_{i} = (x \oplus y)$ in the input tape, we create a new clause $d_{i} = (x \oplus \rightharpoondown y)$ into the output tape, where $x$ and $y$ are literals. Moreover, for each clause of one literal $c_{i} = (x)$ in the input tape, we create the same clause $d_{i} = (x)$ into the output tape, where $x$ is a literal. Hence, we can create a new instance $\psi$ of $\textit{XOR 2SAT}$ as the conjunction of the $d_{i}$ clauses for every clause $c_{i}$ in $\phi$, such that $\psi = d_{1} \wedge \ldots \wedge d_{m}$. Finally, we obtain that:
\[\phi \in \textit{TAGAP 2SAT} \textit{ if and only if } \psi \in \textit{XOR 2SAT}.\]
Consequently, we prove $\textit{TAGAP 2SAT} \leq_{l} \textit{XOR 2SAT}$ where we already know the language $\textit{XOR 2SAT} \in L$ \cite{AR00}, \cite{RM08}. Since $L$ is closed under logarithmic space reductions, then we obtain that $\textit{TAGAP 2SAT} \in L$ \cite{Pap03}.
\end{proof}

\begin{lemma}
\label{nl-complete}
We have the complement of $TAGAP$ complies with $coTAGAP \in \textit{NL--complete}$.
\end{lemma}

\begin{proof}
This is trivially true since $NL$ is closed under complement \cite{Pap03}.
\end{proof}

\begin{theorem}
\label{reduction}
$coTAGAP \leq_{l} \textit{TAGAP 2SAT}$.
\end{theorem}

\begin{proof}
Given a directed graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$, for each edge $(x, y)$ in the input tape from left to right, we create a new clause $(x \oplus y)$ for an instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape, where $x$ and $y$ are positive literals represented by the positive integers $x$ and $y$ which are two nodes in $G$. In addition, before we generate the first clause from the edges, then we create the clause $(\rightharpoondown s)$ into the output tape, and after we generate all the clauses, then we create the clause $(t)$ into the output tape from the IN and OUT nodes of the possible path $s, t \in V$: This is possible because an instance of $\textit{XOR 2SAT}$ have clauses of at most two literals \cite{AR00}.
We can see the final instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape will be topologically sorted, since we create the clauses through the edges from left to right with the exception of $(\rightharpoondown s)$ that is the first clause and $(t)$ that is the last one in $\phi$. Hence, if $\phi$ is an acceptance instance of $\textit{TAGAP 2SAT}$, then there is no a possible path from $s$ to $t$ in $G$, because it is necessary that $s$ and $t$ must be false and true on the clauses $(\rightharpoondown s)$ and $(t)$, respectively. Certainly, if there is path from $s$ to $t$, then $s$ and $t$ should be both true or both false in order the instance $\phi$ of $\textit{TAGAP 2SAT}$ could be possible accepted. Finally, we obtain that:
\[G \in coTAGAP \textit{ if and only if } \phi \in \textit{TAGAP 2SAT}.\]
Consequently, we prove $coTAGAP \leq_{l} \textit{TAGAP 2SAT}$ \cite{Pap03}.
\end{proof}

\begin{theorem}
\label{equal-L}
$L = NL$.
\end{theorem}

\begin{proof}
A single language in $\textit{NL--complete}$ that is logarithmic space reduced to another language $L$, it is sufficiently to prove $L = NL$, since $L$ and $NL$ are closed under logarithmic space reduction \cite{Pap03}. Therefore, this is direct result from Lemma \ref{nl-complete} and Theorem \ref{reduction}.
\end{proof}

\begin{proof}
This is a direct consequence of Theorems \ref{equal-NP} and \ref{equal-L}.
\end{proof}

\begin{theorem}
$L = NP$.
\end{theorem}

\begin{proof}
The $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, because of every problem in $coNP$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}. Certainly, every $coNP$ problem could be logarithmic space reduced to $UNSAT$ by the Cook's Theorem algorithm and $UNSAT$ can be indeed logarithmic space reduced to $3UNSAT$ \cite{GJ79}. Since we have that $L = NL = coNL$ is true, then the complexity class $L$ is equal to $NP$.
\end{proof}

@@

There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems. For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}. Efficient solutions to these problems have enormous implications for logistics \cite{CS00}. Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.

>>>>

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency. However, a precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. The answer P = NP is considered as a very unlikely event. However, we prove the complexity class P is equal to NP.
\end{abstract}

@@

It is fully expected that $P \neq NP$ \cite{Pap03}. Indeed, if $P = NP$ then there are stunning practical consequences \cite{Pap03}. Certainly, $P$ versus $NP$ is one of the greatest open problems in science and a correct solution for this incognita will have a great impact not only in computer science, but for many other fields as well \cite{AS17}. Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}. We show some results that prove this outstanding problem with the unexpected solution of $P = NP$.

@@

@@

@@

\section{Hypothesis}

The two-way Turing machines may move their head on the input tape into two-way (left and right directions) while the one-way Turing machines are not allowed to move the input head on the input tape to the left \cite{KU15}. Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}. They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions \cite{HM81}. Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$ \cite{HM81}.

@@

\begin{theorem}
\label{coNL}
A language $L_{1}$ is in $coNL$ if and only if $L_{1}$ complies with there is a nondeterministic logarithmic space Turing machine $M_{1}$, such that for every appropriate instance $x$, then all the paths on $M_{1}(x)$ accept when $x \in L_{1}$ or at least one of the paths on $M_{1}(x)$ rejects when $x \notin L_{1}$.
\end{theorem}

\begin{proof}
The proof is simple, since we can interchange the acceptance and rejection states of $M_{1}$ into a new Turing machine $M_{1}'$, such that $M_{1}'(x) = ``yes"$ when $M_{1}(x) = ``no"$ and $M_{1}'(x) = ``no"$ when $M_{1}(x) = ``yes"$. Certainly, the language $L(M_{1}')$ is the complement of $L_{1}$ and it is in $NL$ according to the definition of $NL$ and because of the string $x$ is an appropriate instance \cite{Pap03}.
\end{proof}

\begin{theorem}
\label{pos-implication}
When the Hypothesis \ref{hypothesis2} is true, then $P = NP$.
\end{theorem}

\begin{proof}
We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis2} by a nondeterministic logarithmic space Turing machine $N$ such that $N(w) = y$, since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}. Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}. We remove each symbol generated in the work tapes, when we try to generate the next symbol contiguous to the right on the string $u$. In this way, the generation will always be in logarithmic space. In addition, we can guarantee that the generation of symbols in the work tapes always produces an appropriated string $u$, since we can check this by symbol per symbol from the generated string $u$.

Since we have that $L_{1} \in 1NL$, then we can accept the elements of the language $L_{1}$ by a nondeterministic one-way logarithmic space Turing machine $M'$. In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will accept when $w \in L_{2}$ for all the possible paths and will reject when $w \notin L_{2}$ for at least one of the paths.

The reason is because we can simulate the output string of $N(w)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}. Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the nondeterministic one-way logarithmic space Turing machine $M'$. Actually, the logarithmic space reduction is possible, because of $M'$ is in one way. Indeed, it is not necessary to reset the computation of $N$ in the composition $M'(N(w))$ on the input $w$, because $M'$ never moves to the left the head on the input tape (that would be the output tape of $N$).

As a consequence of Theorem \ref{coNL}, then $L_{2}$ would be in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$ \cite{Pap03}. If any single $\textit{coNP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{Pap03}. Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that the Hypothesis \ref{hypothesis2} is true.
\end{proof}

@@

\begin{proof}
Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right. We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$. While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause from left to right. In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $\textit{SUM--ZERO}$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$. Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
\[\phi \in 3UNSAT \Leftrightarrow (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value, respectively. Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output. This logarithmic space disqualification will be the Algorithm \ref{algorithm2}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$. In addition, we reject immediately when the following comparisons:
\[A[i] < 1 \vee A[i] > 3\]
hold at least into one single binary digit. Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$. In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.
\end{proof}

\begin{algorithm}
\caption{Logarithmic space disqualifier}\label{algorithm2}
\begin{algorithmic}[1]
\Comment{A valid instance for $3UNSAT$ with its disqualification}
\Procedure{$\textit{DISQUALIFIER}$}{$\phi, A$}
\Comment{Initialize an index}
\State $j \gets 0$
\Comment{$m$ is the number of clauses in $\phi$}
\Comment{Iterate for the elements of the disqualification array $A$}
\For{$i$}{$1$}{$m + 1$}
\If{$i = m+1$}
\Comment{There exists an $m+1$ element in the array}
\If{$A[i] \neq \textit{undefined}$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\EndIf
\Comment{Break the $\textbf{for}$ loop}
\State \textbf{break}
\ElsIf{$A[i] = \textit{undefined} \vee A[i] < 1 \vee A[i] > 3$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\Else
\State $j \gets A[i]$
\EndIf
\Comment{From the indexed $i^{th}$ clause $c_{i} = (x_{j} \vee y_{k} \vee z_{r})$ in $\phi$}
\Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
\Comment{Output the integer representation of the $j^{th}$ literal, that is $n(x_{j})$}
\Comment{Filled with zeroes to the left until a total of $|3 \times m|$ bits including the literal}
\Comment{But, the bit-length of the symbol minus is ignored in filling the negated literals}
\State \textbf{output} $``\ , \ n(x_{j})"$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\begin{proof}
This is a direct consequence of Theorems \ref{1nl} and \ref{demonstration}.
\end{proof}

@@

@@

There are positive consequences that will follow from rendering tractable many currently mathematically intractable problems. For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}. Efficient solutions to these problems have enormous implications for logistics \cite{CS00}. Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.
